Artin Group Presentations Arising from Cluster Algebras

### 2014-08-12 Paper.tex
edited acknowledgements

\title{Artin Group Presentations Arising from Cluster Algebras}
\author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
\address{you can put addresses for authors\\
 \\
Jacob: 225 St. Edward's Hall; Notre Dame, IN 46556 \\
Hailee: 1184 W Main St; Decatur, IL 62522 }
\email{jhaley3@nd.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
\date{\today}
\keywords{Artin group, cluster algebra, diagram representations}

@@

\section{Acknowledgements}
\thanks{This work was supported by the RTG grant NSF/DMS-1148634. We'd also like to thank the University of Minnesota School of Mathematics for hosting us, and we'd like to thank Gregg Musiker and Emily Gunawan for their useful comments on our work.

>>>>

\title{Artin Group Presentations Arising from Cluster Algebras}
\author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
\address{Jacob: 225 St. Edward's Hall; Notre Dame, IN 46556 \\
Hailee: 1184 W Main St; Decatur, IL 62522}
\email{jhaley3@nd.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
\date{\today}
\keywords{Artin group, cluster algebra, diagram representations}

@@

\section{Acknowledgements}
\thanks{This work was supported by the RTG grant NSF/DMS-1148634. We would also like to thank the University of Minnesota School of Mathematics for hosting us. We are greatly appreciative of Gregg Musiker's mentoring, support, and guidance on this problem. We thank Emily Gunawan for her useful comments on our work. We also thank Vic Reiner for helping Gregg Musiker pose the problem.}
